\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.725in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{fancyhdr}
\usepackage{amsfonts}
\usepackage{color}
\usepackage[british]{babel}
\usepackage[colorlinks]{hyperref}
\usepackage{array} % for defining a new column type
\usepackage{varwidth} %for the varwidth minipage environment
\usepackage{longtable}
\title{Algorithm Identifier List}
\author{Lo Kam Tao Leo\\leolo@leolo.org}
\date{\today}
\setcounter{tocdepth}{1}
\setlength{\headheight}{15.2pt}
\pagestyle{fancy}
\newcommand{\see}[1]{[\ref{#1}]}
\newcommand{\hex}[1]{\texttt{0x#1}}
\begin{document}
	\newcolumntype{M}{>{\begin{varwidth}{7cm}}l<{\end{varwidth}}} %M is for Maximal column
	\tableofcontents
	\vspace{25.4mm}
	\noindent
	Copyright \textcopyright 2018, LO Kam Tao Leo
	All rights reserved.
	
	Redistribution and use in source and binary forms, with or without
	modification, are permitted provided that the following conditions are met:
	\begin{itemize}
		\item Redistributions of source code must retain the above copyright notice, this
		list of conditions and the following disclaimer.
		
		\item Redistributions in binary form must reproduce the above copyright notice,
		this list of conditions and the following disclaimer in the documentation
		and/or other materials provided with the distribution.
		
		\item Neither the name of the copyright holder nor the names of its
		contributors may be used to endorse or promote products derived from
		this software without specific prior written permission.
	\end{itemize}

	
	THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS ``AS IS''
	AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
	IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE
	DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT HOLDER OR CONTRIBUTORS BE LIABLE
	FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
	DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR
	SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER
	CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY,
	OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE
	OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
	\section{Preface}
	The key words ``MUST'', ``MUST NOT'', ``REQUIRED'', ``SHALL'', ``SHALL
	NOT'', ``SHOULD'', ``SHOULD NOT'', ``RECOMMENDED'',  ``MAY'', and
	``OPTIONAL'' in this document are to be interpreted as described in
	RFC 2119.
	\section{Hash algorithm}
		\begin{longtable}{|lcr||M|l|}
			\hline 
			\multicolumn{3}{|c||}{Identifier} &  Algorithm name & Remarks \\\hline \endhead
			\hex{0000}&-&\hex{fdff}&\textit{Unallocated}&  \\\hline
			\hex{fe00}&-&\hex{feff}&Implementation specific algorithm& \see{h:1}\\\hline
			\hex{ff00}&-&\hex{ffff}&Reserved for future expansion&  \\\hline 
		\end{longtable} 
		\begin{enumerate}
			\item \label{h:1}Implementations MAY use this block of identifiers for algorithm that does not have any identifier allocated to it.
		\end{enumerate}
	\section{Encryption algorithm}
		\begin{longtable}{|lcr||c|M|l|}
			\hline 
			\multicolumn{3}{|c||}{Identifier} & Cipher Type & Algorithm name & Remarks \\ 
			\hline \endhead
			\hex{0000}&-&\hex{4fff}&  &\textit{Unallocated}&  \\\hline 
			\hex{5000}&&& BLOCK & Null cipher& \see{en:1} \\\hline 
			\hex{5001}&&& STREAM&Null cipher& \see{en:1} \\\hline  
			\hex{5002}&-&\hex{fdff}&  &\textit{Unallocated}&  \\\hline 
			\hex{fe00}&-&\hex{feff}&  &Implementation specific algorithm& \see{en:2} \\\hline 
			\hex{ff00}&-&\hex{ffff}&  &Reserved for future expansion&  \\\hline
		\end{longtable} 
		\begin{enumerate}
			\item \label{en:1}Null cipher is not recommended to be used as it does not actually encrypt the
			data. Implementation SHOULD provide warning for using these cipher.
			\item \label{en:2}Implementations MAY use this block of identifiers for algorithm that does not have any identifier allocated to it.
		\end{enumerate}
	\section{Key derivation algorithm}
		\begin{longtable}{|lcr||M|l|}
			\hline 
			\multicolumn{3}{|c||}{Identifier} &  Algorithm name & Remarks \\\hline \endhead
			\hex{0000}&-&\hex{fdff}&\textit{Unallocated}&  \\\hline
			\hex{fe00}&-&\hex{feff}&Implementation specific algorithm& \see{kd:1}\\\hline
			\hex{ff00}&-&\hex{ffff}&Reserved for future expansion&  \\\hline 
		\end{longtable}
		\begin{enumerate}
			\item \label{kd:1}Implementations MAY use this block of identifiers for algorithm that does not have any identifier allocated to it.
		\end{enumerate}
\end{document}